### 2022-04-20 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@28c85b6732c2e44e4483ff56e8f0bb79c1f65c3f 🚀

For every species pool, we measured its Local Contribution to
Beta-Diversity (Legendre and De Cáceres 2013); LCBD works from a
species-data matrix (traditionally noted as Y), where species are rows
and sites are columns, and a value of 1 indicates occurrence. We
extracted the Y matrix assuming that every pixel represents a unique
location, and following best practices (Legendre and Condit 2019)
transformed it using Hellinger's distance to account for unequal bat
richness at different pixels. The correction of raw community data is
particularly important for two reasons: first, it prevents the artifact
of richer sites having higher importance; second, it removes the effect
of overall species richness, which is already incorporated in the
phylogenetic diversity component. High values of LCBD indicate that the
pixel has a community that is on average more dissimilar in species
composition than what is expected knowing the entire matrix, i.e.~a more
unique community.

@@

@@

>>>>

For every species pool, we measured its Local Contribution to
Beta-Diversity (Legendre and De Cáceres 2013); LCBD works from a
species-data matrix (traditionally noted as \(\mathbf{Y}\)), where
species are rows and sites are columns, and a value of 1 indicates
occurrence. We extracted the Y matrix assuming that every pixel
represents a unique location, and following best practices (Legendre and
Condit 2019) transformed it using Hellinger's distance to account for
unequal bat richness at different pixels. The correction of raw
community data is particularly important for two reasons: first, it
prevents the artifact of richer sites having higher importance; second,
it removes the effect of overall species richness, which is already
incorporated in the phylogenetic diversity component. High values of
LCBD indicate that the pixel has a community that is on average more
dissimilar in species composition than what is expected knowing the
entire matrix, i.e.~a more unique community. Recent results by Dansereau
et al. (2022) shows that LCBD measures are robust with regards to
spatial scale, and are therefore applicable at the global scale.

@@

\leavevmode\hypertarget{ref-Dansereau2022EvaEco}{}%
Dansereau, G. et al. 2022. Evaluating ecological uniqueness over broad
spatial extents using species distribution modelling. - Oikos n/a:
e09063.

@@

\leavevmode\hypertarget{ref-Legendre2013BetDiv}{}%
Legendre, P. and De Cáceres, M. 2013. Beta diversity as the variance of
community data: Dissimilarity coefficients and partitioning (H Morlon,
Ed.). - Ecology Letters 16: 951--963.

\leavevmode\hypertarget{ref-Legendre2019SpaTem}{}%
Legendre, P. and Condit, R. 2019. Spatial and temporal analysis of beta
diversity in the Barro Colorado Island forest dynamics plot, Panama. -
Forest Ecosystems 6: 7.
